Modelling Stochastic Time Delay for Regression

### 2021-03-21 documentation/article/article.tex
Began the abstract.

\begin{abstract}
... 
\end{abstract}

>>>>

\begin{abstract}
Systems with stochastic time delay between input and output present a number of unique challenges. 
Time domain noise leads to irregular alignments, obfuscates relationships and attenuates inferred coefficients. 
To handle these challenges, we introduce a regression model that considers stochastic time delays as 'errors' in the time domain. For a certain subset of problems, by modelling both prediction and time errors it is possible to outperform traditional models.
Through a simulated experiment, we demonstrate results that significantly improve upon Ordinary Least Squares regression.

\end{abstract}
